---
title: Science Foundation Ireland Grants Commitments
date: '2026-02-24'
categories:
- Sfi Grants
description: Science Foundation Ireland Historical Grants Commitments
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

This week we're exploring Irish STEM research and ancillary projects funded by Science
Foundation Ireland (SFI) since its foundation in 2000 to its dissolution on 31st
July 2024. The data comes from [Ireland's Open Data Portal](https://data.gov.ie/dataset/science-foundation-ireland-grants-commitments)

> SFI was the national foundation in Ireland for investment in scientific and
> engineering research. Consequently, SFI invested in those academic
> researchers and research teams who were most likely to generate new
> knowledge, leading edge technologies and competitive enterprises in the
> fields of science, technology, engineering and maths (STEM).

- Which Higher Education Institute received the most grant funding?
- How much did Science Foundation Ireland invest into research each year?


**Data source:** [Science Foundation Ireland Historical Grants Commitments](https://data.gov.ie/dataset/science-foundation-ireland-grants-commitments)  
**Original article:** [Science Foundation Ireland Historical Grants Commitments](https://data.gov.ie/dataset/science-foundation-ireland-grants-commitments)  
**Curated by:** Cormac Monaghan  

```{r}
#| output: asis
tt_dataset_section("2026-02-24", "sfi_grants", "Sfi Grants")
```
