---
title: Agricultural Production Statistics in New Zealand
date: '2026-02-17'
categories:
- Dataset
description: Gap between people and sheep rapidly closing
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

This week we are exploring [agriculture production statistics in New Zealand](https://figure.nz/table/TSQ8lkuKnyzfERF3) using data compiled from 
from [StatsNZ](https://datainfoplus.stats.govt.nz/item/nz.govt.stats/eb7208cf-2f0f-416a-bd77-2fdbb9043255?_ga=2.264735308.2106648024.1715287902-1399521469.1678132138). 

Sheep have long outnumbered people in New Zealand, but the [ratio of sheep to people peaked in the 1980s and has been in steady decline](https://www.rnz.co.nz/news/country/560252/gap-between-people-and-sheep-rapidly-closing)

> The gap between people and sheep in New Zealand is rapidly closing. There's now about 4.5 sheep to every person in New Zealand compared to a peak of 22 sheep per person in the 1980s, that's according to figures released by Stats NZ this week.

- Is sheep production unique in its decline? Do other types of meat production show the same pattern?
- Which agricultural industries have shown the most production growth?


**Data source:** [Figure.NZ](https://figure.nz/table/TSQ8lkuKnyzfERF3)  
**Original article:** [Gap between people and sheep rapidly closing](https://www.rnz.co.nz/news/country/560252/gap-between-people-and-sheep-rapidly-closing)  
**Curated by:** Jen Richmond  

```{r}
#| output: asis
tt_dataset_section("2026-02-17", "dataset", "Dataset")
```
