---
title: UK Baby Names
date: '2026-06-16'
categories:
- England Wales Names
- Ni Names
- Scotland Names
description: Babies' First Names, 2025
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

This week's dataset explores baby names in the UK. 

There are three datasets which cover baby names across England and Wales from the [Office for National Statistics](https://www.ons.gov.uk/peoplepopulationandcommunity/birthsdeathsandmarriages/livebirths/datasets/babynamesinenglandandwalesfrom1996), Northern Ireland from the [Northern Ireland Statistics and Research Agency](https://www.nisra.gov.uk/publications/baby-names-2025), and Scotland from [National Records of Scotland](https://www.nrscotland.gov.uk/publications/babies-first-names-2025/).

> Dearest gentle reader… we can report that Daphne, Eloise and Penelope have all increased in popularity this year, with the name of each Bridgerton character reaching joint 172nd, 91st, and 71st place respectively, up from 476th, 124th, and 81st in 2024. 

* How does the ranking of most popular names compare between the three datasets?
* Are boys' or girls' names more likely to be unique?
* Can you show the *Bridgerton trend* in charts?


**Data source:** [All Names Given To Babies Between 1974 To 2025](https://www.nrscotland.gov.uk/publications/babies-first-names-2025/, https://www.ons.gov.uk/peoplepopulationandcommunity/birthsdeathsandmarriages/livebirths/datasets/babynamesinenglandandwalesfrom1996, https://www.nisra.gov.uk/publications/baby-names-2025)  
**Original article:** [Babies' First Names, 2025](https://www.nrscotland.gov.uk/publications/babies-first-names-2025/)  
**Curated by:** Nicola Rennie  

```{r}
#| output: asis
tt_dataset_section("2026-06-16", "england_wales_names", "England Wales Names")
```
```{r}
#| output: asis
tt_dataset_section("2026-06-16", "ni_names", "Ni Names")
```
```{r}
#| output: asis
tt_dataset_section("2026-06-16", "scotland_names", "Scotland Names")
```
