---
title: How likely is 'likely'?
date: '2026-03-10'
categories:
- Absolute Judgements
- Pairwise Comparisons
- Respondent Metadata
description: Comparative and Absolute Probability Phrases
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

In an [online quiz](https://probability.kucharski.io/), created as an independent project by Adam Kucharski, over 5,000 participants compared pairs of probability phrases (e.g. “Which conveys a higher probability: Likely or Probable?”) and assigned numerical values (0–100%) to each of 19 phrases. The resulting data can be used to analyse how people interpret common probability phrases.

* Which phrases do people most disagree on, in relation to the probability they represent?
* Which demographic background is the most optimistic?
* Does the order people are shown phrases in change their interpretation?


**Data source:** [Kucharski AJ (2026) CAPphrase: Comparative and Absolute Probability phrase dataset. DOI: 10.5281/zenodo.18750055](https://github.com/adamkucharski/CAPphrase)  
**Original article:** [Comparative and Absolute Probability Phrases](https://adamkucharski.github.io/CAPphrase/)  
**Curated by:** Nicola Rennie  

```{r}
#| output: asis
tt_dataset_section("2026-03-10", "absolute_judgements", "Absolute Judgements")
```
```{r}
#| output: asis
tt_dataset_section("2026-03-10", "pairwise_comparisons", "Pairwise Comparisons")
```
```{r}
#| output: asis
tt_dataset_section("2026-03-10", "respondent_metadata", "Respondent Metadata")
```
