---
title: Bird Sightings at Sea
date: '2026-04-14'
categories:
- Beaufort Scale
- Birds
- Sea States
- Ships
description: At-Sea Observations of Seabirds 1969 to 1990, Tasman Sea, New Zealand
  and Australian waters
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

This week we're exploring Bird Sightings at Sea! The data this week comes from Te Papa Tongarewa, The Museum of New Zealand. It consists of log book entries of bird sightings at sea near New Zealand, from 1969 to 1990.

Thank you to [David Hood](https://bsky.app/profile/thoughtfulnz.bsky.social) for the [dataset suggestion](https://bsky.app/profile/thoughtfulnz.bsky.social/post/3mdp6dzuaks2d).

> The data was recorded using guidelines for the Australasian Seabird Mapping Scheme and counts seabirds seen from a ship during a 10 minute period. The data includes geolocations of the sightings, bird species, numbers and behaviour, observer and ship name, and observation date and time.

- The data was recorded by hand and split into standardized columns. Do the logbook entries in `species_common_name` in the `birds` dataset always match up with the split columns such as `species_scientific_name`, `age`, `wan_plumage_phase`, `plumage_phase`, and `sex`.


**Data source:** [At-Sea Observations of Seabirds 1969 to 1990](https://catalogue.data.govt.nz/dataset/at-sea-observations-of-seabirds-1969-to-1990)  
**Original article:** [At-Sea Observations of Seabirds 1969 to 1990, Tasman Sea, New Zealand and Australian waters](https://obis.org/dataset/29ea15ed-8f76-40ca-bd14-58c62e10b2ef)  
**Curated by:** Jon Harmon, Data Science Learning Community  

```{r}
#| output: asis
tt_dataset_section("2026-04-14", "beaufort_scale", "Beaufort Scale")
```
```{r}
#| output: asis
tt_dataset_section("2026-04-14", "birds", "Birds")
```
```{r}
#| output: asis
tt_dataset_section("2026-04-14", "sea_states", "Sea States")
```
```{r}
#| output: asis
tt_dataset_section("2026-04-14", "ships", "Ships")
```
