---
title: Golem Grad Tortoise Data
date: '2026-03-03'
categories:
- Clutch Size Cleaned
- Tortoise Body Condition Cleaned
description: Sex Ratio Bias Triggers Demographic Suicide in a Dense Tortoise Population
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

The datasets this week come from the paper "[Sex Ratio Bias Triggers Demographic Suicide in a Dense Tortoise Population](https://onlinelibrary.wiley.com/doi/10.1111/ele.70296)".
This topic seemed so interesting that even media like the New York Times picked it up:
"[Constant Sexual Aggression Drives Female Tortoises to Walk Off Cliffs](https://www.nytimes.com/2026/02/14/science/tortoises-island-sex-cliff.html)".

> In an exceptionally dense island population of Hermann's tortoises 
> in Lake Prespa in North Macedonia, sexually coercive males 
> dramatically overnumber females, inflict severe copulatory injuries 
> and put them at risk of fatal falls from the island plateau's sheer 
> rock faces. Harassed females are emaciated, reproduce less frequently,
> produce smaller clutches and have lower annual survival rates compared 
> to females from a neighbouring mainland population. Sixteen years of 
> capture-recapture data reveal an ongoing extinction event and predict
> that the last island female will die in 2083. 

- Do recaptures happen more often in spring or summer? 
- Does it seem easier to recapture male or female tortoises?
- What are the differences among tortoises from the mainland vs the ones from the island in terms of body mass or carapace length?


**Data source:** [Sex Ratio Bias Triggers Demographic Suicide in a Dense Tortoise Population](https://figshare.com/articles/journal_contribution/Sex_ratio_bias_triggers_demographic_suicide_in_a_dense_tortoise_population/30752687)  
**Original article:** [Sex Ratio Bias Triggers Demographic Suicide in a Dense Tortoise Population](https://onlinelibrary.wiley.com/doi/10.1111/ele.70296)  
**Curated by:** Novica Nakov, Free Software Macedonia  

```{r}
#| output: asis
tt_dataset_section("2026-03-03", "clutch_size_cleaned", "Clutch Size Cleaned")
```
```{r}
#| output: asis
tt_dataset_section("2026-03-03", "tortoise_body_condition_cleaned", "Tortoise Body Condition Cleaned")
```
