---
title: Brazilian Companies
date: '2026-01-27'
categories:
- Companies
- Legal Nature
- Qualifications
- Size
description: Wikipedia's List of largest Brazilian companies
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

This week we’re exploring  **Brazilian Companies**, curated from Brazil’s open **CNPJ (Cadastro Nacional da Pessoa Jurídica)** records published by the **Brazilian Ministry of Finance / Receita Federal** on the national open-data portal ([dados.gov.br](https://dados.gov.br/dados/conjuntos-dados/cadastro-nacional-da-pessoa-juridica---cnpj)).

> The CNPJ open data is a large-scale public registry of Brazilian legal entities. For this dataset, the raw company records were cleaned and enriched with lookup tables (legal nature, owner qualification, and company size), then filtered to retain firms above a share-capital threshold so the analysis focuses on meaningful variation in capital stock.

* Which **legal nature** categories concentrate the highest total and average capital stock?
* How does **company size** relate to capital stock (and how skewed is it)?
* Do specific **owner qualification** groups dominate high-capital companies?
* What patterns emerge when comparing the **top capital-stock tail** across categories (legal nature, size, qualification)?


**Data source:** [Open data CNPJ - December 2025](https://arquivos.receitafederal.gov.br/dados/cnpj/dados_abertos_cnpj/2025-12/)  
**Original article:** [Wikipedia's List of largest Brazilian companies](https://en.wikipedia.org/wiki/List_of_largest_Brazilian_companies)  
**Curated by:** Marcelo Silva  

```{r}
#| output: asis
tt_dataset_section("2026-01-27", "companies", "Companies")
```
```{r}
#| output: asis
tt_dataset_section("2026-01-27", "legal_nature", "Legal Nature")
```
```{r}
#| output: asis
tt_dataset_section("2026-01-27", "qualifications", "Qualifications")
```
```{r}
#| output: asis
tt_dataset_section("2026-01-27", "size", "Size")
```
