---
title: Films Based on Video Games
date: '2026-06-09'
categories:
- Game Films
description: List of films based on video games
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

The dataset this week comes from the Wikipedia article [List of films based on video games](https://en.wikipedia.org/wiki/List_of_films_based_on_video_games). It covers theatrical releases, direct-to-video productions, television films, short films, and documentaries adapted from video games, spanning from the early 1990s to upcoming releases. Each row is a film, with box office figures, critic scores, budgets, and release dates where available.

> The list covers feature films, animated films, live-action films, television films, and short films that are based on or inspired by a video game franchise.

Some questions worth exploring:

- Which video game franchise has generated the most film adaptations, and
  which has earned the most at the box office?
- Which video game publishers have the most film adaptations, and how have they performed at the box office?
- Do audiences and critics agree? Compare CinemaScore grades against
  Rotten Tomatoes scores.


**Data source:** [Wikipedia](https://en.wikipedia.org/wiki/List_of_films_based_on_video_games)  
**Original article:** [List of films based on video games](https://en.wikipedia.org/wiki/List_of_films_based_on_video_games)  
**Curated by:** Georgios Karamanis  

```{r}
#| output: asis
tt_dataset_section("2026-06-09", "game_films", "Game Films")
```
