---
title: Ecotourism
date: '2026-07-28'
categories:
- Occurrences
- Tourism
- Weather
description: Getting Started with the {ecotourism} Package
---

```{r}
#| include: false
source("R/tt_helpers.R")
```

This week we're exploring ecotourism! The [{ecotourism}](https://vahdatjavad.github.io/ecotourism) R package provides tools to analyse ecological observation data alongside weather conditions and tourism data.

> The goal of `ecotourism` is to provide clean, ready-to-use datasets for example analyses in teaching, demos, and reproducible workflows.

* Under which weather conditions are you most likely to observe a Gouldian finch?
* How does weather affect tourism numbers in each region?
* How do observations of the different animals relate to numbers of tourists?

The [{ecotourism}](https://vahdatjavad.github.io/ecotourism) package provides additional datasets and ideas for analsyis. Remember to cite the package with `citation("ecotourism")`!


**Data source:** [{ecotourism} R package](https://github.com/vahdatjavad/ecotourism/)  
**Original article:** [Getting Started with the {ecotourism} Package](https://vahdatjavad.github.io/ecotourism/articles/getting-started.html)  
**Curated by:** Nicola Rennie  

## Occurrences

```{r}
#| output: asis
tt_dataset_section("2026-07-28", "occurrences")
```
## Tourism

```{r}
#| output: asis
tt_dataset_section("2026-07-28", "tourism")
```
## Weather

```{r}
#| output: asis
tt_dataset_section("2026-07-28", "weather")
```
